---
title: "State Summaries: Coming Soon!"
output: flexdashboard::flex_dashboard
---

```{r setup, include=FALSE}
library(flexdashboard)
library(DT)
library(dichromat)
library(RColorBrewer) # display.brewer.pal(n = 9, name = 'Greens')
library(readxl)
library(dplyr)
library(sf)
library(leaflet)

colors <- colorschemes$BluetoOrange.12
region.colors <- colors[c(1:6,11)]

greens9 <- brewer.pal(n = 9, name = "Greens")
greens7 <- brewer.pal(n = 9, name = "Greens")[-c(1:2)]

bgo.cols <- c(colors[c(1:4)], greens7[c(7,6,4,3)], colors[c(12:9)])
```

```{r functions}
# Read Template
templateReadList <- function(path) {
  sheets <- readxl::excel_sheets(path)
  sheets <- sheets[-match(c("Instructions", "Lookups"),sheets)] #Remove Instructions and lookups sheets
  x <- lapply(sheets, function(X)
    readxl::read_excel(
      path,
      sheet = X,
      skip = 1,
      .name_repair = "universal"
    )) |>  #Skip first row of instructions
    setNames(sheets) |> 
    lapply(dropExampleRows)
  x
}

dropExampleRows <- function(table) {
  tail(table, -2)
}

# Read Catalog Data
catalogReadList <- function(path) {
  sheets <- readxl::excel_sheets(path)
  x <- lapply(sheets, function(X)
    readxl::read_excel(
      path,
      sheet = X,
      .name_repair = "universal"
    )) |>  #Skip first row of instructions
    setNames(sheets)
  x
}

# Join Read Data
templateJoin <- function(dataList){
  x <- dataList$Study_Info %>%
    left_join(dataList$Site_Info, by = c("Study.Protocol.ID")) %>%
    left_join(dataList$Plot_Info, by = c("Site.Name", "Study.Protocol.ID", "Plot.Design")) %>%
    full_join(dataList$Surveys, by = c("Site.Plot.ID", "Study.Protocol.ID")) %>%
    left_join(dataList$Observations, by = c("Site.Plot.Survey.ID", "Study.Protocol.ID"))
  x
}


# Read and Process USPVDB, use sf as it is easier to manipulate later, specify CRS to transform into
pvdbRead <- function(crs){
  pvdbDat <- httr::GET(url = "https://eersc.usgs.gov/api/uspvdb/v1/projects") |>
    jsonlite::parse_json(simplifyVector = T) |>
    st_as_sf(coords = c("xlong", "ylat"),
             crs = st_crs("ESRI:102003")) |> 
    st_transform(crs = crs)
}


```


```{r DataRead, include = F}

#Geospatial Datasets
states_poly <- st_read("data/geo/States_coterminous.shp") |> st_transform(crs = st_crs(4326))
fws_poly <- st_read("data/geo/fws_coterminous.shp") |> st_transform(crs = st_crs(4326))
ecoL2_poly <- st_read("data/geo/Eco_L2_coterminous.shp") |> st_transform(crs = st_crs(4326))

#Simulated SolSource Data
#vegDat <- templateReadList("data/simulated_SolSource/Study-JK-lx-860 Vegetation Surveys-Many Visits.xlsx")
#polDat <- templateReadList("data/simulated_SolSource/Study-OJ-gj-672 Pollinator Surveys-Many Sites.xlsx")

```


Summary {}
=======================================================================

#### **`r paste0("Updated ", format(Sys.time(), '%B %d, %Y'))`** {data-height=900}

The tables and figures provided in this data portal sunmmarize the studies that can be found within the SolSource Database. It uses a compiled dataset which can be requested from the datasets catalog. 


Column {data-width=600}
--------------------------------------

### Interactive map with states

```{r}
map <- leaflet::leaflet(states_poly, options = leafletOptions(minZoom = 2, maxZoom = 6)) %>%
  leaflet::addTiles() %>%
  leaflet::setView(lng = -95, lat = 40, zoom = 4) %>%
   leaflet::addPolygons(data = states_poly,  
            color = "black",
            fillOpacity = 0.20,
            labelOptions = labelOptions(style = list("font-size" = "12px")),
            highlight = highlightOptions(color = "white", bringToFront = TRUE), 
            group = "States")

map

```

Column {data-width=300}
-------------------------------------

### Table of species found on site vs off site within the slected state

Species offsite

```{r}

```

### Summaries of the data collection efforts and PV presence occuring in the state

Data Collection Efforts

```{r}

```

